RSV

### 2018-01-20 Analysis/RSV.Rmd
Install rgeos

```{r setup, include=FALSE, error=FALSE, warning=FALSE, message=FALSE}
install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table", "tikzDevice", "splitstackshape"))
library(devtools)
install_github("gavinsimpson/tsgam")
install_github("kassambara/easyGgplot2")
install_github("airbornemint/outbreak-predict")
```
```{r}
source("./RSV.R")
```

>>>>

```{r setup, include=FALSE, error=FALSE, warning=FALSE, message=FALSE}
install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table", "tikzDevice", "splitstackshape", "maps", "mapproj", "rgdal", "rgeos"))
library(devtools)
install_github("gavinsimpson/tsgam")
install_github("kassambara/easyGgplot2")
install_github("airbornemint/outbreak-predict")
```
```{r}
source("./RSV.R")
```
